Test parsing of Proff.no table

### 2022-07-08 Test parsing of Proff table.Rmd
Link to Brønnøysund åpnde data.
Adding currency column.

@@

```{r function_modified}
read_proff2 <- function(file, start, end){
  read_html(file, encoding = "UTF-8") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select(
    REGNSKAPSPERIODE:start) |> 
  mutate(
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
    filter(
      !row_number() > 176
    ) |>
  filter(
    !grepl("Lukk", REGNSKAPSPERIODE)
    ) |> 
  pivot_longer(
    end:start, names_to = "year") |> 
  mutate(
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  filter(
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate(
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate(
    value = as.numeric(value)
  ) |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )
}

Kors <- read_proff2("Links/Kors.html", "2001", "2020") |> 
  arrange(desc(year))
```

### Visualisations
```{r}
Kors |> 
  filter(REGNSKAPSPERIODE == "Årsresultat") |> 
  ggplot(aes(year, value)) +
  geom_col()

>>>>

# currency
table_kreft6b <- table_kreft6 |> mutate(
  valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA))

table_kreft6b |> 
  fill(valutakode, .direction = "updown")

@@

```{r function_modified}
read_proff2 <- function(file, start, end){
  read_html(file, encoding = "UTF-8") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select( # removing empty column
    REGNSKAPSPERIODE:start) |> 
  mutate( # removing whitespace
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
  filter( # removing duplicate table
      !row_number() > 176
    ) |>
  filter( # removing duplicate rows
    !grepl("Lukk", REGNSKAPSPERIODE)
    ) |> 
  pivot_longer( # tidying data
    end:start, names_to = "year") |> 
  mutate( # changing to real NAs and turning years into numbers
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  mutate( # adding currency column
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |> 
  fill( # filling the currency column
    valutakode, .direction = "updown"
    ) |> 
  filter( # removing dates and redundant currency
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate( # removing whitespace in numbers
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate( # turning into numbers
    value = as.numeric(value)
  ) |> 
  mutate( # removing years as values
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )
}

Kors <- read_proff2("Links/Kors.html", "2001", "2020") |> 
  arrange(desc(year))

Kors
```

### Basic visualisations
```{r}
Kors |> 
  filter(REGNSKAPSPERIODE == "Årsresultat") |> 
  ggplot(aes(year, value)) +
  geom_col()
